### 2017-01-11 robust-software.tex
Fixup typo from pull request #43
Fixup awkward sentence from PR #42

Users will want to change some values more often than others.
Which ones is software-specific and so cannot be detailed here,
but a short list includes input and reference files and directories,
output files and directories,
filtering parameters,
random number generation seeds,
and
alternatives such as compressing results,
use a variant algorithm,
or verbose output.

@@

The same tools can and should be used to manage runtime environments on users' machines as well.
Accordingly,
developed should
\textbf{document all dependencies in a machine-readable form}.
Package managers like apt and yum are available on most Unix-like systems, and
application package managers exist for specific languages like Python (pip),
Java (Maven/Gradle), and Ruby (RubyGems). These package managers can be used
together with the build utility to ensure that dependencies are available at
compile/run time.

>>>>

Users will want to change some values more often than others.
Since parameters are software-specific, the appropriate 'tunable' ones cannot be detailed here,
but a short list includes input and reference files and directories,
output files and directories,
filtering parameters,
random number generation seeds,
and
alternatives such as compressing results,
use a variant algorithm,
or verbose output.

@@

The same tools can and should be used to manage runtime environments on users' machines as well.
Accordingly,
developers should
\textbf{document all dependencies in a machine-readable form}.
Package managers like apt and yum are available on most Unix-like systems, and
application package managers exist for specific languages like Python (pip),
Java (Maven/Gradle), and Ruby (RubyGems). These package managers can be used
together with the build utility to ensure that dependencies are available at
compile/run time.
